|

### 2019-08-28 paper.Rmd
Rewriting of the introduction.

A good way to visualize high-dimensional data is to display a smooth sequence of interpolated lower dimensional projections. This is called a tour [@As85; @BCAH05] and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. A limitation of this approach is that concavities in a distribution may be hidden when looking at projections. A simple example are projections of samples on a hypersphere. No projection of such a distribution allows to distinguish a hollow sphere from a full one. On the other hand, the difference would be obvious when looking at a slice through the center of the sphere.

>>>>

Modern data is typically high-dimensional and thus data visualisation often relies on some form of dimension reduction. This entails looking at (non-)linear projections of the data. Interactive and dynamic displays often provide information beyond what can be achieved in a static display. For example, the grand tour [@As85; @BCAH05] shows a smooth sequence of interpolated lower dimensional projections and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. Additionaly, we may complement projections with section information. This is often possible in interactive graphics systems by means of brushing [@ggobiCSDA2003;@JSSv081i05], where the user is selecting a region in a subspace of the dataspace that is highlighted in a projection of the data points.

The complementarity between projections and sections has previously been discussed in @prosection, dubbing the combination "prosections". These prosections allow the identification of lower-dimensional structure embedded in the high-dimensional space. One simple example is that prosections can reveal the difference between a full and hollow hypersphere. In addition to hollowness (concave structures) they can also provide a clear picture of internal structures that may be concealed in a projection. For example, @prosection uses prosections to reveal the internal structure of the four-point ultrametric locus [@locus].

Since existing approaches to sectioning are interactive, they rely on the user to redefine the section many times to explore the data. While this level of control is often preferred, it is impractical for detecting and exploring unknown structures in a dataset. As a result smaller hidden features that are only visible in specific sections of the full distribution may easily be missed. In addition having a dynamic approach to sectioning, similar to the grand tour approach to projections, will provide the viewer with context allowing to extrapolate e.g. the shape of a concave structure. We therefore propose a more systematic approach to sectioning based on interpolated projections obtained with a grand tour. The method defines a slice based on 2-d projections provided by the tour and will presents the viewer with an interpolated sequence of slices when running a tour.

The relevant definitions and an overview of the implementation in R are given in Section XXX, and in Section XXX. We then apply the newly defined slice tour to several examples in Section XXX. We consider different high-dimensional geometric shapes and XXX, showing how concave structures can be visualised and explored with a slice tour. Possible extensions are discussed in Section XXX.

<!--
A good way to visualize high-dimensional data is to display a smooth sequence of interpolated lower dimensional projections. This is called a tour [@As85; @BCAH05] and allows to extrapolate the high-dimensional shape of the distribution. It is particularly useful for detecting clusters, outliers and non-linear dependence. A limitation of this approach is that concavities in a distribution may be hidden when looking at projections. A simple example are projections of samples on a hypersphere. No projection of such a distribution allows to distinguish a hollow sphere from a full one. On the other hand, the difference would be obvious when looking at a slice through the center of the sphere.
